\documentclass[../NFTComp_IEEE.tex]{subfiles}
\graphicspath{{\subfix{../Images}}}

\begin{document}
\section{Related Works}
\label{sec:related_works}
Non-Fungible Tokens were introduced about a decade ago with the Quantum project and got a boost when Ethereum and smart contracts appeared \cite{Exmundo2023}. Even considering such small temporal window, the research community did produce a significant number of relevant publication that used NFTs in some capacity. The authors in \cite{Hung2023}, \cite{Barbuta2024}, and \cite{Sharma2024} explore a tokenisation approach to manage real estate, where houses, apartments, land plots, etc. are abstracted by NFTs. Real estate properties are unique and individual, similar to NFTs, and the blockchain mechanics that regulate these tokens are very similar to how real estate markets operate. \cite{Chiacchio2022} follows a similar approach where they use NFTs to abstract pharmaceutical products and use a \textit{digital twin} approach to ensure the traceability by mirroring the lifecycle of a NFTs within a blockchain with the real product. This tokenisation trend continues with \cite{Karandikar2021}, where a similar strategy is used to propose a energy management system for microgeneration. The authors developed a blockchain-based environment where NFTs abstract actors in the system, i.e., solar panels, battery packs, wind turbines, consumers, utility companies, etc. and the values exchanged in the system, i.e., electric energy and money, are abstracted with fungible tokens instead (cryptocurrencies). \cite{Regner2019} provides another example where an event management system uses NFTs to abstract event tickets, taking advantage of the same uniqueness and individual elements, such as allocated seat, event name, id number, etc, to individualise the token by encoding them into the metadata.
\par
Others opted for a higher lever approach and presented an analysis based on the architectural aspects of NFTs rather than use them as a simple building block in a solution. \cite{Hong2019} explores the architectural aspects of specific NFT implementations in the Hyperledger environment, a framework to develop private custom blockchains. \cite{Yang2022} and \cite{Bal2019} present a similar high level architectural approach but with a specific scope in mind, namely, tracing and value transfer applications. \cite{Wang2021b} and \cite{Ma2023} presented \textit{systematisation of knowledge (SoK)} articles about this technology, but they did not approached any architectural aspects. All publication mentioned thus far used Ethereum and Hyperledger for the examples provided, and none even mentioned Flow as an alternative. In that regard, to the time of this writing, we found no academic publications using Flow as a development platform, let alone exploring if the new architectural approach could benefit their solutions. The few mentions to Flow in academic examples came from review style papers, namely \cite{Wang2021}, \cite{Razi2024}, and \cite{Guidi2023}, the latter providing the most extensive explanation of all.

\subsection{Our Contribution}
This paper presents a detailed exploration of the Flow blockchain as an architectural alternative to implement NFTs. To illustrate the differences, we also use Ethereum as an example of a general-purpose blockchain for comparison. We also present a concrete example of a simple NFT contract using Cadence, the smart contract programming language used in Flow, and compare it to a Solidity version of a functionally equivalent NFT contract. This exercise finalises with the analysis of the results obtained.

\end{document}